%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {\normalsize  Mentor (Part-time)} % Job title
    {\Large Embedded Linux Systems | PN Junction} % Organization
    {\normalsize Remote, Egypt} % Location
    {\normalsize May. 2024 - Present} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsizeMentoring and guiding new trainees in Embedded Linux Systems concepts and project implementation.}
        \item {\normalsizeSupporting students in understanding topics such as Yocto, Device Drivers, and Bash scripting.}
        \item {\normalsize Providing technical advice and code reviews to ensure project success and quality.}
        \item {\normalsize Assisting in building strong foundations in Linux administration and embedded Linux workflows.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize Intern (Embedded Linux)} % Job title
    {\Large PN Junction} % Organization
    {\normalsize Cairo, Egypt} % Location
    {\normalsize Aug. 2023 - Jul. 2024} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsize Gaining expertise in Embedded Linux Systems, focusing on C++, Python, and Bash scripting.}
        \item {\normalsize Hands-on experience with Raspberry Pi, Yocto, Device Drivers, and embedded Linux workflows.}
        \item {\normalsize Working on projects including custom device driver implementation and embedded software development.}
        \item {\normalsizeLearning Rust basics and leveraging monitoring tools for embedded applications.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize IOT Intern} % Job title
    {\newline \Large EME Innovation Hub} % Organization
    {\normalsize Alexandria, Egypt} % Location
    {\normalsize Apr. 2023 - Jul. 2023} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsize Gained hands-on experience with Arduino ESP32 for IoT projects.}
        \item {\normalsize Developed skills in Python programming, IOT concepts, and protocols.}
        \item {\normalsize Explored embedded Linux components, including YOCTO and Buildroot.}
        \item {\normalsize Enhanced proficiency in Linux system administration and embedded workflows.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize PCB Design Intern} % Job title
    {\newline \Large EME Innovation Hub} % Organization
    {\normalsize Alexandria , Egypt} % Location
    {\normalsize JUL. 2022 - Sep. 2022} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\normalsize Designed and analyzed circuits for various hardware projects.}
        \item{\normalsize Learned decision-making processes for design based on cost, performance, and mechanical constraints.}
        \item{\normalsize Developed block diagrams, schematics, and PCB layouts with attention to manufacturing methods.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
{\normalsize Embedded System Software Trainee} % Job title
{\newline \Large IMT-School} % Organization
{\normalsize Cairo , Egypt} % Location
{\normalsize JUL. 2021 - AUG. 2021} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{\normalsize Worked on Atmega32 microcontrollers using C programming.}
    \item{\normalsize Gained knowledge in Embedded Systems concepts and interfacing.}
    \item{\normalsize Explored automotive bus technologies and their applications.\newline}
  \end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
