%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{\normalsize PN Junction Workshops} % Role
{\Large IOT Smart Home System } % Event
{\normalsize Remote, Egypt} % Location
{\normalsize Aug. 2024 } % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Developed a smart home system leveraging Internet of Things (IoT) technologies.}
    \item {Integrated functionalities such as controlling lights, fans, and other appliances via a mobile application.}
    \item {Implemented real-time security and monitoring features using \textbf{Node.js} for backend, \textbf{MongoDB} for database management, and \textbf{React.js} for frontend design.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Graduation Project} % Role
{\Large Infotainment System OS} % Event
{\normalsize Cairo, Egypt } % Location
{\normalsize Aug. 2023, May. 2024} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Developed an infotainment system integrating features like music streaming, navigation (MAPS), voice assistant, messaging, and call functionalities.}
    \item {Implemented \textbf{Android Auto} connectivity, enabling seamless interaction between smartphones and vehicle systems using \textbf{AASDK}.}
    \item {Designed a layered architecture comprising:
      \begin{itemize}
        \item \textbf{HMI Layer}: Included MAPS, Music, Call, Message, and Voice Assistant features.
        \item \textbf{APP Layer}: Integrated \textbf{QT Libraries}, \textbf{RT Audio}, \textbf{AASDK}, \textbf{CMake}, and \textbf{Boost Libraries} for robust application development.
        \item \textbf{OS Layer}: Utilized \textbf{Linux}, a Debian-based image, \textbf{Docker} for containerization, and \textbf{OpenAuto Core} to manage Android Auto functionalities.
        \item \textbf{HW Layer}: Leveraged hardware components including \textbf{Raspberry Pi}, a touchscreen, SD card, and ESP8266 for network communication.
      \end{itemize}
    }
    \item {Designed USB and Some/IP communication protocols to establish data transfer between \textbf{Phone}, \textbf{Raspberry Pi 4b}, and \textbf{Touch screen}.}
    \item {Deployed \textbf{OTA updates} using a web-based server to ensure continuous software improvement and feature upgrades.}
    \item {Enabled Android Auto authentication through phone connections and built GPIO interfaces for custom functionalities.}
    \item {Ensured compatibility with external services such as GPS data providers, music streaming platforms, and an OTA server over \textbf{4G LTE/WIFI} networks.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize  PN Junction Projects } % Role
{\Large FOTA (Firmware Over-the-Air) } % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize May. 2024} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
     \item {Implemented a C++ application to handle firmware updates for IoT systems with seamless user experience and robust error handling.}
    \item {Used Raspberry Pi to download and manage firmware updates, ensuring version consistency, integrity, and system reboot.}
   % \item {Incorporated secure communication protocols (HTTPS/SSL) to prevent unauthorized access during firmware update processes.}
    \item {Developed rollback mechanisms to restore the system to the last stable version in case of update failures.}
    \item {Tested the solution on multiple IoT devices to ensure scalability and compatibility across platforms.}
    \item {Optimized memory usage and minimized update time to improve performance on resource-constrained devices.}
    \item {Integrated a web-based interface for remote monitoring and controlling of update campaigns.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize PN Junction Projects } % Role
{\Large PC Control via Phone} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Feb. 2024} % Date(s)
{\setstretch{1.25}
    \begin{cvitems} % Description(s)
        \item {Developed a system to control a PC using a mobile application through the \textbf{API Tester} app.}
    \item {Wrote \textbf{C++} code to implement functionalities for executing system-level commands remotely.}
    \item {Created a server-client architecture where the mobile app acted as a client sending requests to the PC.}
    \item {Used RESTful APIs for communication between the mobile app and the PC, ensuring secure and efficient data exchange.}
    \item {Designed use cases like file operations, media control (e.g., play/pause videos), and basic automation of repetitive tasks.}
    \item {Enabled compatibility with both Wi-Fi and Bluetooth protocols for flexible connectivity options.}
    \item {Tested the solution on multiple devices and operating systems to ensure cross-platform functionality.}
    \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize PN Junction Projects} % Role
{\Large Python Assistant Device (Alexa)} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Oct. 2023} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {Designed an intelligent assistant device using Python to process and respond to voice or text commands with pre-defined functionalities.}
    \item {Integrated features for controlling smart home devices like lights, fans, and security systems using \textbf{IoT protocols}.}
    \item {Implemented natural language processing (NLP) techniques to enhance the device's ability to understand user queries.}
    \item {Used APIs to connect the assistant device to external services such as weather updates, news feeds, and task scheduling.}
    \item {Deployed the device on a \textbf{Raspberry Pi} for portability and integration with other hardware sensors and actuators.}
    \item {Ensured voice feedback functionality by integrating \textbf{text-to-speech (TTS)} libraries and enabling smooth two-way communication.}
      \end{cvitems}
}  
%---------------------------------------------------------
\cventry
{\normalsize Flutter Application for Car} % Role
{\Large Flutter Development} % Event
{\normalsize Remote, Egypt} % Location
{\normalsize Mar. 2024} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {Designed and developed a mobile application for controlling in-car features using \textbf{Flutter}.}
    \item {Implemented the user interface (UI) with an intuitive design for ease of use in a car environment.}
    \item {Integrated functionalities for music playback, navigation, and camera access to provide a seamless in-car experience.}
    \item {Developed a home screen layout with customizable options for quick access to important features.}
    \item {Enabled remote access to control and monitor car features via mobile, allowing users to interact with the car system on the go.}
    \item {Integrated navigation system with real-time map data and turn-by-turn directions for a smoother driving experience.}
    \item {Implemented camera functionality to allow users to monitor car surroundings or use the camera as a rear-view system.}
    \item {Ensured cross-platform compatibility with both Android and iOS devices, leveraging Flutter's capabilities.}
    \item {Used Flutter packages for media playback, location services, and hardware interactions with car systems.}
      \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize EME Innovation Hub} % Role
{\Large Biofuel System} % Event
{\normalsize Alexandria, Egypt} % Location
{\normalsize 2023} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
         \item {Developed Arduino Mega code to manage five relays controlling a pump, motors, sensors, and a load cell.}
      \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize EME Innovation Hub} % Role
{\Large Digital Alarm Clock } % Event
{\normalsize Alexandria, Egypt} % Location
{\normalsize MAY. 2022} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {Developed a digital alarm clock using drivers for AVR-ATMEGA32 controller.}
    \item {Integrated hardware modules like \textbf{LCD}, \textbf{Keypad}, and \textbf{ADC} for input/output functionalities.}
      \end{cvitems}
}  
%---------------------------------------------------------
\cventry
{\normalsize Embedded IMT Projects} % Role
{\Large Smart Home System} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Aug. 2021} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Created a smart home prototype utilizing AVR-ATMEGA32.}
    \item {Used drivers for components like \textbf{Stepper Motor}, \textbf{LCD}, and \textbf{Keypad} for controlling devices.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Embedded IMT Projects} % Role
{\Large Clinic Management System} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Aug. 2021} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Built a clinic management system using C with linked lists and file handling.}
    \item {Implemented a user-friendly interface utilizing Windows APIs for enhanced usability.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Embedded IMT Projects} % Role
{\Large Calculator} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Sep. 2021} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {\normalsize Implemented a calculator using AVR-ATMEGA32 drivers.}
    \item {\normalsize Utilized DIO and keypad for input and LCD for output display.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{\normalsize Embedded IMT Projects} % Role
{\Large Drivers Development for AVR-ATMEGA32} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Oct. 2021} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {\normalsize Created drivers for AVR-ATMEGA32 controllers based on static software.}
    \item {\normalsize Included support for DIO, ADC, LCD, and KPAD peripherals.}
  \end{cvitems}
}


%---------------------------------------------------------
\end{cventries}
